Multi-channel Kondo model URG

### 2021-11-05 multi-channel-urg.tex
wrote down final RG equation in symmetric form by requiring the asymmetric terms to vanish

\documentclass{revtex4-2}
\usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist}
\numberwithin{equation}{section}
\allowdisplaybreaks
\begin{document}
\title{Multi-channel Kondo model URG}
\author{Abhirup Mukherjee}
\date{\today}
\maketitle
\section{Introduction}
The multi-channel Kondo model is described by the Hamiltonian
\begin{equation}\begin{aligned}
	H = \sum_{k,\alpha,\gamma}\epsilon_{k}^\gamma \hat n^\gamma_{k\alpha} + J\sum_{kk^\prime,\gamma} \vec{S_d}\cdot\vec{s}_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime}~.
\end{aligned}\end{equation}
It is mostly identical to the single-channel Kondo model: \(k,k^\prime\) sum over the momentum states, \(\alpha,\alpha^\prime\) sum over the spin indices and \(\gamma\) sums over the various channels. \(\vec S_d, \vec s\) are the impurity and conduction bath spin vectors. The renormalization at step \(j\) is given by
\begin{equation}\begin{aligned}
	\Delta H_j = \left\{c^\dagger T, \eta \right\} = \left(c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c + T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T\right)
\end{aligned}\end{equation}
\begin{equation}\begin{aligned}
	c^\dagger T = J \sum_{k < \Lambda_j, \alpha}\vec{S_d}\cdot\vec{s}_{\beta \alpha}c^\dagger_{q\beta}c_{k\alpha}, &&&H_D = \epsilon_q \tau_{q\beta} + J S_d^z s_q^z
\end{aligned}\end{equation}
Usually we treat the \(\hat \omega\) as number(s) and study the renormalization in the couplings as functions of the quantum fluctuation scales. Each value of the fluctuation scale defines an eigendirection of \(\hat \omega\). We have then essentially traded off the complexity in the non-commutation of the diagonal and off-diagonal terms for all the directions in the manifold of \(\hat \omega\).

@@

	\Delta H^{(2)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D}T^\dagger c}_\text{first term}~ -~ \underbrace{T^\dagger c \frac{1}{\omega - H_D}c^\dagger T}_\text{second term}

@@

We will now simplify the terms individually. The first term is simpler:

@@

@@

	S_d^a S_d^z S_d^b = \left(\frac{1}{4}\delta^{az} + \frac{i}{2}\sum_c \epsilon^{azc}S_d^c\right)S_d^b = \left(\frac{1}{4}\delta^{az}S_d^b + \frac{i}{8} \epsilon^{azb}  - \frac{1}{4}\sum_{c_1,c} \epsilon^{azc_1} \epsilon^{c_1 b c} S_d^c\right) = \frac{1}{4}\left(\delta^{az}S_d^b - \delta^{ab}S_d^z + \delta^{bz}S_d^a\right) + \frac{i}{8}\epsilon^{azb}

@@

We will drop the last numerical term because such a term cannot renormalize the Hamiltonian. Substituting this gives

@@

\subsection{First term}
\begin{align}
	c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c = J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime} c^\dagger_{q\beta} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\beta \alpha} \frac{1}{\omega^\prime - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \beta}
\end{align}
Here the intermediate state is unoccupied, so we put \(\tau = -\frac{1}{2}, s_q^z = -\frac{\beta}{2}\) and since the initial state was occupied, we put \(\epsilon_q = D\).
\begin{align}
	c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c &= \sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{J^2}{\omega^\prime - \frac{1}{2}D + J \frac{\beta}{2}S_d^z }c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta} \\
							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{\left(\omega^\prime - \frac{1}{2}D\right) - J \frac{\beta}{2}S_d^z }{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta}\\
							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) + J \frac{\beta}{2}S_d^z}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} c_{q\beta} S_d^b s^b_{\alpha^\prime \beta} & \left[c_k c^\dagger_{k^\prime} \sim - c^\dagger_{k^\prime}c_k\right] \\
							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) + J \frac{\beta}{2}S_d^z}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\alpha^\prime \beta} \hat n_{q\beta} \\
							   &= J^2 n_j \sum_{\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a s^a_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) + J S_d^z \frac{1}{2}\beta}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^b s^b_{\alpha^\prime \beta}
\end{align}
We again simplify the terms individually, calling them term 1 and term 2. Term 1 can be made identical in form to term 1 using the relation: \(s^b s^a = -s^b s^a \text{ for } a \neq b\). With this change, term 3 becomes
\begin{equation}\begin{aligned}
	\label{term3}
	\text{term 1} = \frac{J^2 n_j \left(\omega^\prime - \frac{1}{2}D\right)}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}\sum_{k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^a  S_d^b \left(s^a s^b\right)_{\alpha^\prime \alpha} = \frac{1}{2}\frac{J^2 n_j \left(\omega^\prime - \frac{1}{2}D\right)}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
\end{aligned}\end{equation}
For term 2, we will use eq.~\ref{identity_SSS} to get
\begin{equation}\begin{aligned}
	\label{term4}
	\text{term 2} = \frac{J^3 n_j }{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \frac{1}{4}\sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \left(\vec{S_d}\cdot\vec{s}_{\alpha^\prime\alpha} -S_d^z \sum_\beta \beta s^a_{\alpha^\prime\beta} s^a_{\beta\alpha} \right)
\end{aligned}\end{equation}

\subsection{Total renormalization \(\Delta H^{(2)}\)}
From the formula for the renormalization \(\Delta H^{(2)}\), we write
\begin{equation}\begin{aligned}
	\Delta H^{(2)} = \text{term 1} + \text{term 2} + \text{term 3} + \text{term 4}
\end{aligned}\end{equation}
These four terms are given by eqs.~\ref{term1}, \ref{term2}, \ref{term3} and \ref{term4}.
From the constraints of URG and particle-hole symmetry, we have the constraint \(\omega + \omega^\prime = H_d^0 + H_d^1\). \(H_d^0\) is the diagonal part when the current node is unoccupied and \(H_d^1\) is when its occupied. For our case, \(H_d^0 + H_d^1 = \sum \epsilon_q \tau_q = D\), because both the hole and particle states have energy of \(\frac{D}{2}\) (\(\epsilon_q\) and \(\tau\) flip sign together). We therefore have \((\omega - D/2) = -(\omega^\prime - D/2)\). With this relation, we have \(\text{term 2} = \text{term 4}\) and \( \text{term 3} = -\text{term 1}\). The total renormalization at second order is therefore
\begin{equation}\begin{aligned}
	\Delta H^{(2)} = -2 \times \text{term 3} = -\frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
\end{aligned}\end{equation}
which gives
\begin{equation}\begin{aligned}
	\Delta J^{(2)} = -\frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}
\end{aligned}\end{equation}
For \(\omega < D/2\), we get the flow towards the strong-coupling fixed point. That is, there is an attractive stable fixed point at \(J^* = 4|\omega - D/2|\) for all bare \(J > 0\). We also get a decay towards the local moment fixed point \(J^* = 0\) for \(J < 0\). For \(\omega = -D/2\) and \(J \ll D\), we get the one-loop PMS form. 
\begin{equation}\begin{aligned}
	\Delta J^{(2)} = \frac{J^2 n_j D}{D^2 - \frac{1}{16}J^2} \simeq \frac{J^2 n_j }{D}
\end{aligned}\end{equation}
\section{Next-to-leading order renormalization}
\begin{equation}\begin{aligned}
	\Delta H^{(3)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c}_\text{first term} ~+~ \underbrace{T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T}_\text{second term}
\end{aligned}\end{equation}

@@

\subsection{Second term}
\begin{equation}\begin{aligned}
	&T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T\\
	&= \sum_{q, k, k^\prime, k_1,k_2,\atop{\beta, \alpha, \alpha^\prime, \alpha_1,\alpha_2,\atop{l_1,l_2,a,b,c}}}c^\dagger_{k^\prime\alpha^\prime, l_1} c_{q\beta, l_1}  S_d^c s^c_{\alpha^\prime \beta} \frac{J^2}{\omega - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \frac{J}{\omega - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z} c^\dagger_{q\beta,l_1} c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha}
\end{aligned}\end{equation}
We take similar steps as before:
\begin{inparaenum}
	\item \(\epsilon_q \tau_{q\beta} = \frac{D}{2}\)
	\item \(s^z_q = \frac{\beta}{2}\)
	\item Sum over \(q\) to get \(n_j\)
	\item Contract \(k\alpha,k^\prime\alpha^\prime\) to get \(K N_j n_j\)
	\item Compute the internal product to obtain \(\mathcal{C}_1^b S_d^b - \mathcal{C}_2^b\)
\end{inparaenum}.
The expression at this point is
\begin{equation}\begin{aligned}
	\label{Cb1Cb2_2}
	\frac{J^3 K N_j n_j }{2\left[\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \sum_{\beta,\alpha, \atop{a,b,c}}s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta} S_d^c \left(\mathcal{C}_1^b S_d^b - \mathcal{C}_2^b\right) S_d^a
\end{aligned}\end{equation}
\(\mathcal{C}^b_1\) is exactly the same as before, the only difference being \(\omega\) replaces \(\omega^\prime\). The sign of \(\mathcal{C}^b_2\) has also flipped, because \(\beta \to -\beta\). The other difference is that \(S_d^a\) and \(S_d^c\) have switched places. Eq.~\ref{Cb1Cb2} is replaced by
\begin{equation}\begin{aligned}
	\label{Cb1Cb2_3}
	\sum_{\beta,\alpha, \atop{a,b,c}}s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta}\left[\frac{1}{4}\mathcal{C}_1^b \left(\delta^{ab}S_d^c - \delta^{ac}S_d^b + \delta^{bc}S_d^a\right) + \mathcal{C}_2^b \frac{i}{2}\sum_{e}\epsilon^{ace}S_d^e\right]
\end{aligned}\end{equation}
Note that even though \(\mathcal{C}^b_2\) came with a minus sign in eq.~\ref{Cb1Cb2_2}, that minus sign has been canceled by a second minus sign that arises from the exchange of \(a \leftrightarrow c\) in \(\epsilon^{cae}\). Since eq.~\ref{Cb1Cb2_3} is identical to eq.~\ref{Cb1Cb2}, we can dirctly write down the renormalization in this case:
\begin{equation}\begin{aligned}
	\label{third_term_2}
	-\frac{1}{16}\frac{J^3 K N_j n_j }{\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2} + \frac{J^4 K N_j n_j \left( \omega - D/2 - J/4 \right) }{32\left[\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}} c^\dagger_{k_1 \alpha_1,l_2}c_{k_2 \alpha_2,l_2}S_d^z s^z_{\alpha_1\alpha_2}
\end{aligned}\end{equation}

\subsection{Total renormalization \(\Delta H^{(3)}\)}
We will again use the relation \(\omega - D/2 = -(\omega^\prime - D/2)\). The total renormalization at this order is obtained by adding eqs.~\ref{third_term_1} and \ref{third_term_2}.
\begin{equation}\begin{aligned}
	\Delta H^{(3)} = -\frac{J^3 K N_j n_j / 8}{\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2} - \frac{J^5 K N_j n_j / 64}{\left[\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}} c^\dagger_{k_1 \alpha_1,l_2}c_{k_2 \alpha_2,l_2}S_d^z s^z_{\alpha_1\alpha_2}
\end{aligned}\end{equation}

>>>>

\documentclass{revtex4-2}
\usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist}
\numberwithin{equation}{section}
\allowdisplaybreaks
\begin{document}
\title{Multi-channel Kondo model URG}
\author{Abhirup Mukherjee}
\date{\today}
\maketitle
\section{Introduction}
The multi-channel Kondo model is described by the Hamiltonian
\begin{equation}\begin{aligned}
	H = \sum_{k,\alpha,\gamma}\epsilon_{k}^\gamma \hat n^\gamma_{k\alpha} + J\sum_{kk^\prime,\gamma} \vec{S_d}\cdot\vec{s}_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime}~.
\end{aligned}\end{equation}
It is mostly identical to the single-channel Kondo model: \(k,k^\prime\) sum over the momentum states, \(\alpha,\alpha^\prime\) sum over the spin indices and \(\gamma\) sums over the various channels. \(\vec S_d, \vec s\) are the impurity and conduction bath spin vectors. The renormalization at step \(j\) is given by
\begin{equation}\begin{aligned}
	\Delta H_j = \left(c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c - T^\dagger c \frac{1}{\hat \omega - H_D}c^\dagger T\right)
\end{aligned}\end{equation}
\begin{equation}\begin{aligned}
	c^\dagger T = J \sum_{k < \Lambda_j, \alpha}\vec{S_d}\cdot\vec{s}_{\beta \alpha}c^\dagger_{q\beta}c_{k\alpha}, &&&H_D = \epsilon_q \tau_{q\beta} + J S_d^z s_q^z
\end{aligned}\end{equation}
Usually we treat the \(\hat \omega\) as number(s) and study the renormalization in the couplings as functions of the quantum fluctuation scales. Each value of the fluctuation scale defines an eigendirection of \(\hat \omega\). We have then essentially traded off the complexity in the non-commutation of the diagonal and off-diagonal terms for all the directions in the manifold of \(\hat \omega\).

@@

	\Delta H^{(2)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D}T^\dagger c}_\text{first term}~+~\underbrace{T^\dagger c \frac{1}{\omega - H_D}c^\dagger T}_\text{second term}

@@

We will now simplify the terms individually. The first term, labelled term 3, is simpler:

@@

	\label{term3_def}

@@

	S_d^a S_d^z S_d^b = \left(\frac{1}{4}\delta^{az} + \frac{i}{2}\sum_c \epsilon^{azc}S_d^c\right)S_d^b = \left(\frac{1}{4}\delta^{az}S_d^b + \frac{i}{8} \epsilon^{azb}  - \frac{1}{4}\sum_{c_1,c} \epsilon^{azc_1} \epsilon^{c_1 b c} S_d^c\right) = \frac{1}{4}\left(\delta^{az}S_d^b - \delta^{ab}S_d^z + \delta^{bz}S_d^a\right)

@@

We have dropped a numerical term because such a term cannot renormalize the Hamiltonian. Substituting this gives

@@

	c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c = J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime} c^\dagger_{q\beta} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\beta \alpha} \frac{1}{\omega^\prime - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \beta}
Here the intermediate state is unoccupied, so we put \(\tau = -\frac{1}{2}, s_q^z = -\frac{\beta}{2}\) and since the initial state was occupied, we put \(\epsilon_q = D\).
	c^\dagger T \frac{1}{\hat \omega - H_D}T^\dagger c &= \sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^b s^b_{\beta \alpha} \frac{J^2}{\omega^\prime - \frac{1}{2}D + J \frac{\beta}{2}S_d^z }c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^a s^a_{\alpha^\prime \beta} \\
							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c_{k\alpha} S_d^b s^b_{\beta \alpha} \frac{\left(\omega^\prime - \frac{1}{2}D\right) - J \frac{\beta}{2}S_d^z }{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}c^\dagger_{k^\prime\alpha^\prime} c_{q\beta} S_d^a s^a_{\alpha^\prime \beta}\\
							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{q\beta} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^b s^b_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) + J \frac{\beta}{2}S_d^z}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} c_{q\beta} S_d^a s^a_{\alpha^\prime \beta} & \left[c_k c^\dagger_{k^\prime} \sim - c^\dagger_{k^\prime}c_k\right] \\
							   &= J^2\sum_{q\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} S_d^b s^b_{\beta \alpha} \frac{-\left(\omega^\prime - \frac{1}{2}D\right) + J \frac{\beta}{2}S_d^z}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^a s^a_{\alpha^\prime \beta} \hat n_{q\beta} \\
							   &= J^2 n_j \sum_{\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} s^a_{\alpha^\prime \beta}s^b_{\beta \alpha} S_d^b \frac{-\left(\omega^\prime - \frac{1}{2}D\right) + J S_d^z \frac{1}{2}\beta}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} S_d^a 
We again simplify the terms individually, calling them term 1 and term 2. 
	\text{term 1} = \frac{-\left(\omega^\prime - \frac{1}{2}D\right)J^2 n_j} {\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} s^a_{\alpha^\prime \beta}s^b_{\beta \alpha} S_d^b S_d^a
Since this term will renormalize only for \(a \neq b\), we can use \(S_d^b S_d^a = -S_d^a S_d^b\). This gives
	\text{term 1} = \frac{\left(\omega^\prime - \frac{1}{2}D\right)J^2 n_j} {\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{\beta k k^\prime \alpha \alpha^\prime a b} c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} s^a_{\alpha^\prime \beta}s^b_{\beta \alpha} S_d^a S_d^b
This is identical to term 3 (eq.~\ref{term3_def}) except for the change \(\omega^\prime \to \omega\). Copying the result from term 3, we get
	\label{term3}
	\text{term 1} = -\frac{1}{2}\frac{J^2 n_j \left(\omega^\prime - \frac{1}{2}D\right)}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
The other term is
	\text{term 2} = \frac{1}{2}\frac{J^3 n_j}{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{\beta k k^\prime \alpha \alpha^\prime a b} \beta c^\dagger_{k^\prime\alpha^\prime}c_{k\alpha} s^a_{\alpha^\prime \beta}s^b_{\beta \alpha} S_d^b S_d^z S_d^a 
From eq.~\ref{identity_SSS}, we know that \(S_d^b S_d^z S_d^a =  S_d^a S_d^z S_d^b\), which means this term is again identical to its counterpart, term 4.
	\label{term4}
	\text{term 2} = \frac{J^3 n_j }{\left(\omega^\prime - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \frac{1}{4}\sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \left(\vec{S_d}\cdot\vec{s}_{\alpha^\prime\alpha} -S_d^z \sum_{a \beta} \beta s^a_{\alpha^\prime\beta} s^a_{\beta\alpha} \right)

\subsection{Total renormalization \(\Delta H^{(2)}\)}
From the formula for the renormalization \(\Delta H^{(2)}\), we write
\begin{equation}\begin{aligned}
	\Delta H^{(2)} = \text{term 1} + \text{term 2} + \text{term 3} + \text{term 4}
\end{aligned}\end{equation}
These four terms are given by eqs.~\ref{term1}, \ref{term2}, \ref{term3} and \ref{term4}. Since the Hamiltonian has particle-hole and \(\mathrm{SU}(2)\) symmetry, we will impose these symmetries by choosing the relation between \(\omega\) and \(\omega^\prime\) such that \(\text{term 2} = \text{term 4}\) and \( \text{term 3} = -\text{term 1}\). The total renormalization at second order is therefore
\begin{equation}\begin{aligned}
	\Delta H^{(2)} = -2 \times \text{term 3} = -\frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2} \sum_{k k^\prime \alpha \alpha^\prime,c} c^\dagger_{k^\prime\alpha^\prime} c_{k\alpha} \vec{S_d}\cdot\vec{s}_{\alpha^\prime \alpha}
\end{aligned}\end{equation}
which gives
\begin{equation}\begin{aligned}
	\Delta J^{(2)} = -\frac{J^2 n_j \left(\omega - \frac{1}{2}D\right)}{\left(\omega - \frac{1}{2}D\right)^2 - \frac{1}{16}J^2}
\end{aligned}\end{equation}
For \(\omega < D/2\), we get the flow towards the strong-coupling fixed point. That is, there is an attractive stable fixed point at \(J^* = 4|\omega - D/2|\) for all bare \(J > 0\). We also get a decay towards the local moment fixed point \(J^* = 0\) for \(J < 0\). For \(\omega = -D/2\) and \(J \ll D\), we get the one-loop PMS form. 
\begin{equation}\begin{aligned}
	\Delta J^{(2)} = \frac{J^2 n_j D}{D^2 - \frac{1}{16}J^2} \simeq \frac{J^2 n_j }{D}
\end{aligned}\end{equation}
\section{Next-to-leading order renormalization}
\begin{equation}\begin{aligned}
	\Delta H^{(3)}_j = \underbrace{c^\dagger T \frac{1}{\omega^\prime - H_D} H_X \frac{1}{\omega^\prime - H_D} T^\dagger c}_\text{first term} ~-~ \underbrace{T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T}_\text{second term}
\end{aligned}\end{equation}

@@

\subsection{Second term}
\begin{equation}\begin{aligned}
	&T^\dagger c \frac{1}{\omega - H_D} H_X \frac{1}{\omega - H_D} c^\dagger T\\
	&= \sum_{q, k, k^\prime, k_1,k_2,\atop{\beta, \alpha, \alpha^\prime, \alpha_1,\alpha_2,\atop{l_1,l_2,a,b,c}}}c^\dagger_{k^\prime\alpha^\prime, l_1} c_{q\beta, l_1}  S_d^c s^c_{\alpha^\prime \beta} \frac{J^2}{\omega - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z} S_d^b s^b_{\alpha_1 \alpha_2} c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \frac{J}{\omega - \epsilon_q\tau_{q\beta} - J S_d^z s_q^z} c^\dagger_{q\beta,l_1} c_{k\alpha,l_1} S_d^a s^a_{\beta \alpha}
\end{aligned}\end{equation}
We take similar steps as before:
\begin{inparaenum}
	\item \(\epsilon_q \tau_{q\beta} = \frac{D}{2}\)
	\item \(s^z_q = \frac{\beta}{2}\)
	\item Sum over \(q\) to get \(n_j\)
	\item Contract \(k\alpha,k^\prime\alpha^\prime\) to get \(K N_j n_j / 2\)
	\item Compute the internal product to obtain \(\mathcal{C}_1^b S_d^b - \mathcal{C}_2^b\)
\end{inparaenum}.
The expression at this point is
\begin{equation}\begin{aligned}
	\label{Cb1Cb2_2}
	\frac{J^3 K N_j n_j }{2\left[\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \sum_{\beta,\alpha, \atop{a,b,c}}s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta} S_d^c \left(\mathcal{C}_1^b S_d^b - \mathcal{C}_2^b\right) S_d^a
\end{aligned}\end{equation}
\(\mathcal{C}^b_1\) is exactly the same as before, the only difference being \(\omega\) replaces \(\omega^\prime\). The sign of \(\mathcal{C}^b_2\) has also flipped, because \(\beta \to -\beta\). The other difference is that \(S_d^a\) and \(S_d^c\) have switched places. Eq.~\ref{Cb1Cb2} is replaced by
\begin{equation}\begin{aligned}
	\label{Cb1Cb2_3}
	\sum_{\beta,\alpha, \atop{a,b,c}}s^a_{\beta \alpha} s^b_{\alpha_1 \alpha_2}s^c_{\alpha \beta}\left[\frac{1}{4}\mathcal{C}_1^b \left(\delta^{ab}S_d^c - \delta^{ac}S_d^b + \delta^{bc}S_d^a\right) + \mathcal{C}_2^b \frac{i}{2}\sum_{e}\epsilon^{ace}S_d^e\right]
\end{aligned}\end{equation}
Note that even though \(\mathcal{C}^b_2\) came with a minus sign in eq.~\ref{Cb1Cb2_2}, that minus sign has been canceled by a second minus sign that arises from the exchange of \(a \leftrightarrow c\) in \(\epsilon^{cae}\). Since eq.~\ref{Cb1Cb2_3} is identical to eq.~\ref{Cb1Cb2}, we can dirctly write down the renormalization in this case:
\begin{equation}\begin{aligned}
	\label{third_term_2}
	-\frac{1}{16}\frac{J^3 K N_j n_j }{\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2} + \frac{J^4 K N_j n_j \left( \omega - D/2 - J/4 \right) }{32\left[\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2\right]^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}} c^\dagger_{k_1 \alpha_1,l_2}c_{k_2 \alpha_2,l_2}S_d^z s^z_{\alpha_1\alpha_2}
\end{aligned}\end{equation}

\subsection{Total renormalization \(\Delta H^{(3)}\)}
Similar to the one-loop case, we will choose the require \(\omega\) and \(\omega^\prime\) to be related such that the  RG equations are \(\mathrm{Su}(2)\) symmetric; that is, we will require the terms that renormalize only \(S_d^z s^z\) vanish. The total renormalization at this order is obtained by adding eqs.~\ref{third_term_1} and \ref{third_term_2}.
\begin{equation}\begin{aligned}
	\Delta H^{(3)} = -\frac{J^3 K N_j n_j / 8}{\left(\omega - \frac{D}{2}\right)^2 - \frac{1}{16}J^2}\sum_{k_1,k_2,\atop{\alpha_1,\alpha_2,l_2}}c^\dagger_{k_1\alpha_1,l_2}c_{k_2 \alpha_2,l_2} \vec{S_d}\cdot\vec{s}_{\alpha_1\alpha_2}
\end{aligned}\end{equation}
Combining with \(\Delta H^{(2)}\), we get
\begin{equation}\begin{aligned}
	\Delta J = \frac{J^2 n_j \left[2 \left(D - 2\omega\right) - \frac{1}{4}J K N_j\right]}{\left(D - 2\omega\right)^2 - \frac{1}{4}J^2}
\end{aligned}\end{equation}
